---
title: "Song analysis workflow"

output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Song Analysis Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup}
library(GrassSongAnalysis)
```
This package can be used to measure, mostly, time related variables in grasshopper song recordings, as well as visualize the songs themselves. The initial recording has to be a `.wav` file.
This package has been used with two *Chorthippus* species, *Ch. biguttulus* in 2017 and *Ch. dorsatus* in 2024. Some functions that where used in 2017 have not been tested recently and they might need to be updated.

The first step to be able to work with the recordings in R is to load them using `loadSongfile()`, which includes the option to apply a high-pass filter.

```{r}
song <- loadSongfile(
 system.file("extdata", "song_raw.wav", package = "GrassSongAnalysis"),
 #path = "yourpath"
 f = NULL,
 highpassfilter=3000, #change this to reflect your needs (units are Hz)
 select = NULL,
 silenceAdd = NULL
)
```


## Workflow for *Chorthippus dorsatus*



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
